An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-04-01 mixedwindow.tex
Rename file with main paper
Remove bootstrap material from paper
This commit is the first real step towards submitting this paper as a note to
Econometrica. It removes the bootstrap material to focus on just the mixed-window
ideas.

@@

\date{March 14, 2013}

@@

\begin{abstract} 
  \noindent This paper proposes a modification of \citepos[\textit{J.
    Econom.}]{ClW:07} adjusted out-of-sample $t$-test.  The
  alternative model is still estimated with a fixed-length rolling
  window, but the benchmark is estimated with a recursive window. The
  resulting statistic is asymptotically normal even when the models
  are nested.  Moreover, the alternative model can be estimated using
  common model selection methods, such as the \aic\ or \bic.  This
  paper also presents a method to compare multiple models
  simultaneously while controlling familywise error, and
  substantially improves existing block bootstrap methods for
  out-of-sample statistics.  This procedure is then used to analyze
  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset.

@@

\section{Introduction} This paper proposes an out-of-sample (\oos)
test statistic that is asymptotically normal with mean zero even when
the models studied are nested.  This paper also proves that common
block bootstrap methods consistently estimate the statistic's
distribution, and shows how the statistic can be used to study many
models simultaneously while maintaining strong control of the
familywise error (\fwe), i.e. ensuring that the probability that the
hypothesis that the model has equal predictive ability to a benchmark
is incorrectly rejected for any of the models is no higher than a
preset level.

\oos\ tests are commonly used in International Macroeconomics,
Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
literature developing the theoretical properties of these statistics,
beginning primarily with \citet{DiM:95} and
\citet{Wes:96}.\footnote{Other papers in this literature include
  \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
  \citet{ClM:01,ClM:05-2,ClM:05,ClM:11b,ClM:12,ClM:12b},
  \citet{CCS:01}, \citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00},
  \citet{InK:04,InK:06}, \citet{Han:05}, \citet{Ros:05},
  \citet{ClW:06,ClW:07}, \citet{Ana:07}, \citet{GiR:09,GiR:10},
  \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11}, \cite{Pin:11},
  \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among others.  For recent
  reviews of this literature and additional references, see
  \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06}, \citet{ClM:11c},
  \citet{CoD:11}, and \citet{Gia:11}} In a pair of papers,
\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
that a small benchmark model is correctly specified.  Their test
compares the forecasting performance of a pair of nested models, and
the null hypothesis is that the innovations in the smaller model form
a martingale difference sequence.  This test procedure is popular, and
one assumes that this is due in part to the statistic's convenience,
the statistic is approximately normal after adjusting for the
estimation error of the larger model.  Normality comes from a
fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
centers the statistic appropriately.  This statistic is especially
convenient because other \oos\ tests for similar hypotheses
(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
and \citealt{Mcc:07}; among others) have a nonstandard limit
distribution and place restrictions on the models under consideration,
while other asymptotically normal statistics test a different null
hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
that are often violated in empirical work (\citealt{DiM:95};
\citealt{Wes:96}; \citealt{WeM:98};
\citealt{Mcc:00}).\footnote{\citet{DiM:95} assume that the models are
  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
  implicitly assume that the models do not converge to the same limit,
  which rules out nesting.}

@@

Since researchers often have a set of potential models and want to
know which of them significantly outperform the benchmark, procedures
that compare a single pair of models are of limited practical value.
As \citet{Whi:00} demonstrates, looking at the naive $p$-values of
individual tests is misleading, but researchers can obtain a valid test
by using the bootstrap to approximate the distribution of the largest
individual test statistic under the null (White calls this procedure
the \textit{Bootstrap Reality Check} or \brc).  This paper presents a test
for equal predictive ability of multiple models based on
\citepos{RoW:05} StepM, which uses a step-down procedure that
iteratively rejects models to achieve higher power than the \brc\ and
indicate which of the models improves on the benchmark (see
Theorem~\ref{res:2} for details).

This paper also presents a new result for the validity of block
bootstraps with \oos\ statistics, which is necessary to verify that
the StepM is valid.  Existing results on bootstrapping \oos\
statistics have some drawbacks.  \citet{Whi:00} and \citet{Han:05} use
the stationary bootstrap, but require the test sample to be much
smaller than the training sample, which obviously does not hold here.
\citet{CoS:07} relax that requirement, but make the statistic more
complicated than necessary by adjusting the objective function of the
bootstrapped statistic to center it correctly.\footnote{Their
  recentering is required for consistency and does not imply higher
  order accuracy.}  A parametric bootstrap, such as that used by
\cite{Mar:95}, \cite{Lut:99}, and \citet{ClM:12b}, is an alternative
method, but requires the benchmark model to be correctly specified.
Although I focus on the null hypothesis that the benchmark is
correctly specified, this paper's block bootstrap methods remain valid
when the benchmark is misspecified and are relatively easy to
implement.  So this paper's result for bootstrapping \oos\ statistics
considerably improves on existing procedures.

The next section presents our new statistics and Section~\ref{sec:1b}
our block bootstrap result.  Section~\ref{sec:2} presents
simulations that compare our pairwise \oos\ test to \poscw\ original
statistics.  Section~\ref{sec:3} demonstrates the use of our statistic
by reanalyzing \citepos{GoW:08} study of excess return
predictability. Section~\ref{sec:4} concludes.

@@

This paper uses \citepos{RoW:05} StepM procedure, which is an iterated
extension of \citepos{Whi:00} Reality Check designed to reject as many
false hypotheses as possible while achieving \sfwe.  Their method
relies on the bootstrap to estimate the joint dependence between the
test statistic associated with each model.  The bootstrap used in this
paper is new, and is outlined in Algorithm~\ref{alg:1}.
Algorithm~\ref{alg:1} actually presents a more general version of the
bootstrap that remains valid with a misspecified benchmark model.
Imposing the null hypothesis of \mds\ leads to simpler version that
will be discussed later.
\begin{alg}\label{alg:1}
  Suppose that there are $m$ alternative forecasting models,
  $\hat{y}_{1t},\dots, \hat{y}_{mt}$, and define the data matrices
  $\X_\R = (X_1,\dots,X_R)'$ and $\X_{\p} = (X_{R+1},\dots,X_{T-1})$
  with
  \begin{equation*}
    X_t = \begin{cases}
      (y_{t+1}, x_t')' & t \leq R \\
      (y_{t+1}, x_t', \hat{y}_{1,t+1}, \dots, \hat{y}_{m,t+1})' & t > R.
    \end{cases}
  \end{equation*}
  \begin{enumerate}
  \item Draw $B$ samples of $P$ observations from $\X_{\p}$ using the
    moving or circular blocks bootstrap with block length $b$ or the
    stationary bootstrap with geometric block lengths with success
    probability $p$.  Denote each sample as $\X_{\p, l}^{*}$ and let
    $\X_l^{*} = [\X_{\R}', \X_{\p,l}^{*\prime}]'$.
  \item Estimate $\bar{f}^{*}_{li}$ and $\hat{\sigma}_{li}^{*}$ as in
    Theorem~\ref{res:1} for each bootstrap sample, $\X^{*}_l$, and each
    alternative model, $\hat{y}_{it}$.
  \end{enumerate}
\end{alg}

This procedure exploits the fact that $R$ is finite in
Theorem~\ref{res:1} and that the expected block length will grow with
$T$.  Under these asymptotics, a growing proportion of the
rolling-window forecasts are the same if we bootstrap the forecasts as
if we bootstrap the empirical data and reestimate the models.
Bootstrapping the forecasts makes the computations faster and easier,
but requires us to drop the first $R$ observations from the bootstrap
(the alternative forecasts are not defined for the first $R$
observations).  I add those observations to the beginning of each
bootstrap sample so that population means under the bootstrap-induced
probability distribution equal sample means.\footnote{This equality is
  strictly true only for the stationary and circular block
  bootstraps.}  The benchmark model still needs to be reestimated in
each bootstrap sample.

@@

\begin{rem}\label{rem:01}
  \citet{Pin:11} raises the issue that, since there are often several
  models that could be used as the benchmark, researchers may want to
  control for data snooping over the null hypotheses as well as the
  alternatives.  For example, one could use either \citepos{AtO:01}
  random walk or \citepos{StW:07} \textsc{ima}(1,1) as benchmark
  inflation models, so it might make sense to require an alternative
  model to outperform them both.\footnote{\citet{Pin:11} studies tests
    that reject if the alternative model outperforms either of the
    models, so the details are somewhat different in our papers.}
  Allowing multiple benchmark models can be expressed as an
  Intersection-Union test, so Theorem~\ref{res:2}'s procedure
  (conclusion~\ref{it:3}) easily accommodates this extension by taking
  each $\bar f_i$ and $\hat{\sigma}_{i}^{2}$ to be a random
  $q$-vector;\footnote{If a researcher uses multiple benchmark models,
    it would be a mistake to assume that they are all correctly
    specified, so only the null hypothesis of conclusion~\ref{it:3} is
    appropriate.} the first element of $\bar f_{i}$, written as $\bar
  f_{i1}$, compares the first benchmark model to the $i$th alternative
  and the first element of $\hat{\sigma}_i^2$ is the corresponding
  estimate of asymptotic variance, the second element corresponds to
  the second benchmark model, etc.

  Steps 1 and 2 of Theorem~\ref{res:2}'s procedure now become:
  \begin{enumerate}
  \item Define $M_0 = \emptyset$ and, for $j = 1,\dots,m$, let $M_j =
    \{(i,k): \tfrac1{\hat\sigma_{ik}} \bar{f}_{ik} > \hat{d}_j\}$,
    where $\hat{d}_j$ is the $1 - \alpha$ quantile of $\max_{(i,k)
      \notin M_{j-1}} \tfrac1{\hat\sigma_{ik}^*} \big(\bar{f}_{ik}^{*} -
    \bar{f}_{ik}(\hat{\beta}_{k,T+1})\big)$.
  \item Reject all of the hypotheses $H_i$ such that $(i,k) \in
    \bigcup_{j=1}^m M_j$ for all $k$.
  \end{enumerate}
  Also note that the asymptotic variance-covariance matrix of each
  $\bar f_i$ does not need to be positive definite as long as the
  variance of each of its elements is positive.  A formal statement of
  this result is given in Appendix~\ref{sec:B}.
\end{rem}

\section{The Bootstrap for Out-of-Sample Statistics}\label{sec:1b}
The validity of the bootstrap in Theorem~\ref{res:2} is a special case
of a result of independent interest---the validity in general of block
bootstraps for asymptotically normal \oos\ statistics.  This section
presents the general result.  In this section, let $\to^{p^{*}}$ and
$\to^{d^{*}}$ refer to convergence in probability or distribution
conditional on the observed data.  Similarly, $\E^{*}$, $\var^{*}$,
and $\cov^{*}$ refer to the expectation, variance, and covariance with
respect to the probability measure induced by the bootstrap, and
$y_t^{*}$, etc. is the random variable $y_t$ but under the
bootstrap-induced \cdf.

The notation in this section is more general than that of
Section~\ref{sec:1}.  The assumptions required are generalizations of
the conditions of Theorems~\ref{res:1} and~\ref{res:2}.  See
\citet{Wes:96,Wes:06}, \citet{WeM:98}, and \citet{Mcc:00} for a
discussion of these conditions, as theirs are nearly identical.
Theorem~\ref{res:3} gives the result.

\begin{thm}\label{res:3}
  Suppose the following conditions hold:
  \begin{enumerate}
  \item The estimator $\hat{\beta}_t$ of $\btrue$ is estimated with a
    recursive, rolling, or fixed estimation window and satisfies
    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
    a sequence of $k \times q$ matrices such that $\sup_t |\hat{B}_t -
    B| \to^p 0$; $H_{t}$ is a sequence of $q$-vectors such that
    \begin{equation}
      H_{t} = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s}(\btrue) & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s}(\btrue) & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s}(\btrue) & \text{fixed window} \\
      \end{cases}
    \end{equation}
    and $\E h_{s}(\btrue) = 0$ for all $s$.
  \item Define $\psi_t(\beta) = (f_t(\beta), h_t(\beta))$;
    $\psi_t(\beta)$ is covariance stationary and twice continuously
    differentiable in an open neighborhood $N$ of $\btrue$.  Also,
    $\E \sup_{\beta \in N} |\psi_t(\beta)|^r$ and $\E\sup_{\beta \in
      N} |\frac{\partial}{\partial \beta} \psi_t(\beta)|^r$ are
    uniformly bounded, and there exists a sequence of random variables
    $m_t$ such that $\sup_{i,\beta \in N} |\tfrac{\partial^2}{\partial
      \beta \partial \beta'} \psi_{it}(\beta)| \leq m_t$ almost surely
    and $\E m_t^2$ is uniformly finite.
  \item Both $\psi_t(\beta)$ and $\frac{\partial}{\partial \beta}
    \psi_t(\beta)$ are $L_2$-\ned\ of size $-\frac12$ on the
    series $V_t$ with bounded \ned-coefficients for $\beta$ uniformly
    in $N$; $V_t$ is strong mixing of size $-\frac{r}{r-2}$ or uniform
    mixing of size $-\frac{r}{2r-2}$ with $r > 2$.\footnote{For
      uniform mixing processes, $r = 2$ is also allowed as long as
      $\sup_{\beta \in N} \psi_t(\beta)^2$ and $\sup_{\beta \in N}
      (\partial \psi_t(\beta) / \partial \beta)^2$ are uniformly
      integrable.}
  \item The sequence $\hat f_1^{*},\dots,\hat f_T^{*}$ is constructed
    using the same procedure as the original \oos\ analysis over the
    bootstrap sample, where the bootstrap sample is generated by
    moving blocks, circular blocks, or stationary bootstrap with block
    lengths drawn from the geometric distribution.  The (expected)
    block length $b$ satisfies $b \to \infty$ and $\frac{b}{P} \to 0$.
  \item The bootstrapped estimator satisfies $\sup_t |\hat{B}_t^{*} -
    B^{*}| \to^p 0$, $B^{*} = B + o_p$ and $\frac1T \sum_{t=1}^T
    h_t^*(\btrue[*]) = 0$ a.s.
  \item The asymptotic variance matrix of $\bar{f}(\btrue)$ is
    uniformly positive definite.
  \item $R, P \to \infty$ as $T \to \infty$.
  \end{enumerate}
  Then
  \begin{equation}
    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\btrue[*]))
        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\btrue)) \leq x] | >
      \epsilon] \to 0
  \end{equation}
  for all $\epsilon > 0$.
\end{thm}

\begin{rem}
  \citet{Mcc:00} proves asymptotic normality under weaker smoothness
  conditions on $f_t(\beta)$ and $h_t(\beta)$: only their expectations
  must be continuously differentiable.  It may be possible to extend
  Theorem~\ref{res:3} to those weaker conditions, but the current
  proof relies on a theorem of \citepos{JoD:00} establishing the
  consistency of \hac\ estimators and their theorem requires differentiability of
  the observations.  Extending \citepos{JoD:00} result to
  nondifferentiable functions should be possible, but is beyond the
  scope of this paper.
\end{rem}

\begin{rem}
  \citet{Whi:00} and \citet{Han:05} resample the forecasts but do not
  reestimate any of them which requires the additional assumption that
  $\tfrac{P}{R} \log \log R \to 0$ or that the forecasts themselves
  have no estimated parameters.\footnote{\citet{Whi:00} lists several
    different sets of assumptions that give the same result, but these
    seem to be the most general.}
\end{rem}

\begin{rem}
  \citet{CoS:07} use the distribution of $\sqrt{P}(\bar{f}^{*} -
  \bar{f})$ to approximate that of $\sqrt{P}(\bar{f} - \E
  \bar{f}(\btrue))$.  But it is clear that $\bar{f}(\btrue[*])$
  is the bootstrap analogue of $\E \bar{f}(\btrue)$, the parameter of
  interest.  Because their bootstrap is miscentered, \citet{CoS:07}
  must redefine $\hat{\beta}_t^{*}$ to achieve consistency.  In this
  paper, though, consistency arises naturally.
\end{rem}

\begin{rem}
  It may be unnecessary to assume that $\bar{f}(\btrue)$ has positive
  definite asymptotic variance; if so, the bootstrap would work in the
  setup of \citet{ClM:05,ClM:01} and \citet{Mcc:07}.  That question is
  left to future research.
\end{rem}

@@

For comparison, we study this paper's new statistic as well as \poscw
rolling-window and recursive-window test statistics.  Clark and West
only prove that their rolling-window statistic is asymptotically
normal, and only then if the benchmark model is not estimated, but
their recursive-window statistic is popular in practice and in
simulations tends to perform similarly to their rolling window test.
We use all three of these statistics to test the null that the
benchmark model's innovation is an \mds.\footnote{\citet{ClW:07}
  report the performance of the tests proposed by \citet{CCS:01} and
  \citet{ClM:05} as well, and of tests based on the naive Gaussian
  statistic.}

@@

\section{Conclusion}\label{sec:4}
This paper presents an \oos\ test statistic similar to \poscw\ that is
asymptotically normal when comparing nested or non-nested models.
Normality is achieved by estimating the alternative model using a
fixed-length rolling window---as do Clark and West---but estimating
the benchmark model with a recursive window.  Simulations indicate
that the new statistic behaves similarly to Clark and West's original
test when the \dgp\ is stable but can have much higher power when the 
\dgp\ has structural breaks.  The paper also presents a
method for comparing the benchmark model to several alternative models
simultaneously and improves block bootstrap procedures of \oos\
statistics.

@@

Define the additional notation 
$F_t(\beta) = \tfrac{\partial}{\partial \beta} f_t(\beta)$,
$F_t = F_t(\btrue)$,
$\hat f_t^* = f_t^*(\hat\beta_t^*)$,
$F_t^*(\beta) = \tfrac{\partial}{\partial \beta} f_t^*(\beta)$,
$F_t^* = F_t^*(\btrue[*])$,
$h_t = h_t(\btrue)$,
$h_t^* = h_t^*(\btrue[*])$, 
and
\begin{equation*}
      H_{t}^* = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s}^* & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s}^* & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s}^* & \text{fixed window} \\
      \end{cases}
\end{equation*}

@@

\newcommand{\WesA}[1][]{\oclt{t}
  (F_t^{#1} - \E^{#1} F_t^{#1}) B^{#1} H_t^{#1}}
\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1} F_t^{#1} \osum{t} (B_t^{#1} -
  B^{#1}) H_t^{#1}}
\newcommand{\WesC}[1][]{\oclt{t}
  (F_t^{#1} - \E^{#1} F_t^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}
\begin{proof}[Proof of Theorem~\ref{res:3}]
  Expand $f_t^{*}(\hat{\beta}_t^{*})$ around $\btrue[*]$
  to get
  \begin{align*}
    \sqrt{P} \big(\bar{f}^{*} - \bar{f}(\btrue[*])\big) &= \oclt{t}
    \big(f_t^{*} - \bar{f}(\btrue[*])\big) +
    \E^* F_t^{*} B^{*} \oclt{t} H_t^* \\
    & \quad + \WesA[*] + \WesB[*] \\ & \quad + \WesC[*] + \oclt{t} w_t^*
  \end{align*}
  where (as in \citealp{Wes:96}) the $i$th element of $w_t^*$ is
  \begin{equation*}
    w_{it} = \tfrac12 (\hat\beta_t^* - \hat\beta_{T+1})'
    \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'} 
    f_{it}^*(\tilde\beta_{it}^*) \Big]
    (\hat\beta_t^* - \hat\beta_{T+1})
  \end{equation*}
  and each $\tilde\beta_{it}^*$ lies between $\hat\beta_t^*$ and
  $\hat\beta_{T+1}$.  The argument that $\oclt{t} w_t^* = o_{p^*}(1)$ is
  identical to West's, using our Lemma~\ref{res:a2} in place of his
  Lemma A3.  Then
  \begin{gather}
    \WesA[*] \to^{p^*} 0 \label{eq:7} \\
    \WesB[*] \to^{p^*} 0 \label{eq:9} \\
  \intertext{and}
    \WesC[*] \to^{p^*} 0 \label{eq:10}
  \end{gather}
  from Lemma~\ref{res:a4} and the result follows from
  Lemma~\ref{res:a3}, with the form of the asymptotic variance
  following directly from \citet{Wes:96} and \citet{WeM:98}.
\end{proof}

\begin{lem}[Formalization of Remark~\ref{rem:01}]
  Suppose that the conditions of Theorem~\ref{res:2} conclusion~\ref{it:3}
  hold but $f_i = (f_{i1},\dots,f_{iq})$ and the asymptotic variance
  of $(\bar{f}_{1k}(\beta_k),\dots,\bar{f}_{mk}(\beta_k))$ is
  uniformly positive definite for each $k$.  Then the procedure
  described in Remark~\ref{rem:01} achieves \sfwe.
\end{lem}

The proof is similar to that of Theorem~\ref{res:2}. Note that we
allow $\sqrt{P}(\bar{f}_{i1}(\beta_1),\dots,\bar{f}_{iq}(\beta_q))$ to
converge to a normal with singular variance-covariance matrix as long
as each element has positive variance.

@@

\begin{lema}\label{res:a2}
  Suppose $a \in [0,\frac12)$ and the conditions of Theorem~\ref{res:3}
  hold.
  \begin{enumerate}
  \item $P^a \sup_t | H_{t} | \to^p 0$ and $P^a \sup_t | H_{t}^{*} |
    \to^{p^{*}} 0$.
  \item $P^a \sup_t | \hat{\beta}_{t} - \beta_{0} | \to^{p} 0$ and
    $P^a \sup_t | \hat{\beta}^{*}_{t} - \hat{\beta}_T |
    \to^{p^{*}} 0$.
  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t) = O_{p}(1)$
    and $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t^* - \E F_t^*) =
    O_{p^*}(1)$.
  \end{enumerate}
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a2}]
  \begin{enumerate}
  \item The process $\tfrac{1}{\sqrt{T}} h_{s}$ satisfies
    \citepos[Theorem 3.1]{JoD:00b} functional \clt.  So
    \begin{equation}
      P^a \sup_t \Big| \tfrac1t \sum_{s=1}^t h_{s} \Big| =
      P^a \sup_{\gamma \in [0,1]} \Big| \tfrac{1}{\lfloor \gamma
        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s} \Big| \to^{p} 0
    \end{equation}
    with the convergence following from the continuous mapping
    theorem.  For the bootstrapped average, \citepos{Cal:13}
    Theorem~2 ensures that
    \begin{equation}
      \tfrac{1}{\sqrt{\gamma
          T}} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s}^*
      = O_{p^*}(\Omega^*(\hat\beta_{T+1})^{1/2})
    \end{equation}
    where $\Omega^*(\beta) = \var^* h_t^*(\beta)$.  Since
    $\hat\beta_{T+1} \to^p \btrue$, it suffices to show that
    $\sup_{\beta \in N} | \Omega^*(\beta) - \var h_t(\beta) | \to^p
    0$.  But this convergence holds for any fixed $\beta$ and our
    assumptions guarantee stochastic equicontinuity as in
    \citet{JoD:00} \citep[also see][]{Dav:94}, completing the proof.

  \item We have
    \begin{multline}
      P^a \sup_t | \hat{\beta}_t - \btrue | = P^a \sup_t |\hat{B}_{t}
      H_{t}| \\ \leq \sup_{t,u} \Big| [ \hat{B}_u - B]
      \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t} \Big|
      B \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big|
    \end{multline}
    and both terms converge to zero in (conditional) probability by
    the previous argument and by assumption.  The same argument holds
    for $\hat{\beta}_t^{*} - \btrue[*]$ as well.
  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t)$ obeys
    \citepos{Jon:97} \clt, so the result is trivial.  Also,
   \begin{equation}
     \Big\lvert\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T 
     ( F_t^* - \E^* F^*)\Big\rvert = O_{p^*}(\Omega^*(\hat\beta_{T+1})^{1/2}) = O_p(1)
    \end{equation}
    as in the proof of part 1, where now $\Omega^*(\beta) = \var^* F_t^*(\beta)$.
  \end{enumerate}
\end{proof}

>>>>

% These commands are generated when the monte carlo and applied
% sections are run; I'm giving them definitions now so that LaTeX will
% run.
\providecommand\bootsize{[missing]}
\providecommand\empiricalcriticalvalue{[missing]}
\providecommand\nboot{[missing]}
\providecommand\testsize{[missing]}
\providecommand\totalsims{[missing]}
\providecommand\windowlength{[missing]}
\providecommand\empiricaltable{[missing]}

@@

% \date{March 14, 2013}

@@

\begin{abstract} 
  \noindent This paper proposes a modification of \citepos[\textit{J.
    Econom.}]{ClW:07} adjusted out-of-sample $t$-test.  The
  alternative model is still estimated with a fixed-length rolling
  window, but the benchmark is estimated with a recursive window. The
  resulting statistic is asymptotically normal even when the models
  are nested.  Moreover, the alternative model can be estimated using
  common model selection methods, such as the \aic\ or \bic.
  This procedure is then used to analyze
  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset.

@@

\section{Introduction} This paper proposes an out-of-sample (\oos)
test statistic that is asymptotically normal with mean zero even when
the models studied are nested.
\oos\ tests are commonly used in International Macroeconomics,
Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
literature developing the theoretical properties of these statistics,
beginning primarily with \citet{DiM:95} and
\citet{Wes:96}.\footnote{Other papers in this literature include
  \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
  \citet{ClM:01,ClM:05-2,ClM:05,ClM:11b,ClM:12,ClM:12b},
  \citet{CCS:01}, \citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00},
  \citet{InK:04,InK:06}, \citet{Han:05}, \citet{Ros:05},
  \citet{ClW:06,ClW:07}, \citet{Ana:07}, \citet{GiR:09,GiR:10},
  \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11}, \cite{Pin:11},
  \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among others.  For recent
  reviews of this literature and additional references, see
  \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06}, \citet{ClM:11c},
  \citet{CoD:11}, and \citet{Gia:11}} In a pair of papers,
\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
that a small benchmark model is correctly specified.  Their test
compares the forecasting performance of a pair of nested models, and
the null hypothesis is that the innovations in the smaller model form
a martingale difference sequence.  This test procedure is popular, and
one assumes that this is due in part to the statistic's convenience,
the statistic is approximately normal after adjusting for the
estimation error of the larger model.  Normality comes from a
fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
centers the statistic appropriately.  This statistic is especially
convenient because other \oos\ tests for similar hypotheses
(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
and \citealt{Mcc:07}; among others) have a nonstandard limit
distribution and place restrictions on the models under consideration,
while other asymptotically normal statistics test a different null
hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
that are often violated in empirical work (\citealt{DiM:95};
\citealt{Wes:96}; \citealt{WeM:98};
\citealt{Mcc:00}).\footnote{\citet{DiM:95} assume that the models are
  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
  implicitly assume that the models do not converge to the same limit,
  which rules out nesting.}

@@

The next section presents our new statistics and Section~\ref{sec:2} presents
simulations that compare our test to \poscw\ original
statistics.  Section~\ref{sec:3} demonstrates the use of our statistic
by reanalyzing \citepos{GoW:08} study of excess return
predictability. Section~\ref{sec:4} concludes.

@@

[Need to fill in joint normality corollary and StepM procedure.]

@@

@@

For comparison, we study this paper's new statistic as well as \poscw\
rolling-window and recursive-window test statistics.  Clark and West
only prove that their rolling-window statistic is asymptotically
normal, and only then if the benchmark model is not estimated, but
their recursive-window statistic is popular in practice and in
simulations tends to perform similarly to their rolling window test.
We use all three of these statistics to test the null that the
benchmark model's innovation is an \mds.\footnote{\citet{ClW:07}
  report the performance of the tests proposed by \citet{CCS:01} and
  \citet{ClM:05} as well, and of tests based on the naive Gaussian
  statistic.}

@@

\section{Conclusion}\label{sec:4}
This paper presents an \oos\ test statistic similar to \poscw\ that is
asymptotically normal when comparing nested or non-nested models.
Normality is achieved by estimating the alternative model using a
fixed-length rolling window---as do Clark and West---but estimating
the benchmark model with a recursive window.  Simulations indicate
that the new statistic behaves similarly to Clark and West's original
test when the \dgp\ is stable but can have much higher power when the 
\dgp\ has structural breaks.

@@

Define the additional notation 
$F_t(\beta) = \tfrac{\partial}{\partial \beta} f_t(\beta)$,
$F_t = F_t(\btrue)$,
and
$h_t = h_t(\btrue)$.

@@

\newcommand{\WesA}[1][]{\oclt{t}
  (F_t^{#1} - \E^{#1} F_t^{#1}) B^{#1} H_t^{#1}}
\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1} F_t^{#1} \osum{t} (B_t^{#1} -
  B^{#1}) H_t^{#1}}
\newcommand{\WesC}[1][]{\oclt{t}
  (F_t^{#1} - \E^{#1} F_t^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}

@@

\begin{lema}\label{res:a2}
  Suppose $a \in [0,\frac12)$ and the conditions of Theorem~\ref{res:3}
  hold.
  \begin{enumerate}
  \item $P^a \sup_t | H_{t} | \to^p 0$.
  \item $P^a \sup_t | \hat{\beta}_{t} - \beta_{0} | \to^{p} 0$.
  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t) = O_{p}(1)$.
  \end{enumerate}
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a2}]
  \begin{enumerate}
  \item The process $\tfrac{1}{\sqrt{T}} h_{s}$ satisfies
    \citepos[Theorem 3.1]{JoD:00b} functional \clt.  So
    \begin{equation}
      P^a \sup_t \Big| \tfrac1t \sum_{s=1}^t h_{s} \Big| =
      P^a \sup_{\gamma \in [0,1]} \Big| \tfrac{1}{\lfloor \gamma
        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s} \Big| \to^{p} 0
    \end{equation}
    with the convergence following from the continuous mapping
    theorem.
  \item We have
    \begin{equation}
      P^a \sup_t | \hat{\beta}_t - \btrue | = P^a \sup_t |\hat{B}_{t}
      H_{t}| \leq \sup_{t,u} \Big| [ \hat{B}_u - B]
      \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t} \Big|
      B \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big|
    \end{equation}
    and both terms converge to zero in (conditional) probability by
    the previous argument and by assumption.
  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t)$ obeys
    \citepos{Jon:97} \clt, so the result is trivial.
  \end{enumerate}
\end{proof}

\begin{lema}\label{res:a4}
  Under the conditions of Theorem~\ref{res:1}, Equations
  \eqref{eq:11}--\eqref{eq:13} hold.
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a4}]
We can write
\begin{equation*}
  \Big\lvert \WesA \Big\rvert \leq 
  \Big\lvert \oclt{t} (F_t - \E F_t) B \Big\rvert
  \sup_t | H_t |.
\end{equation*}
From Lemma~\ref{res:a2}, $\sup_t | H_t | \to^p 0$ and $\oclt{t}
(F_t - \E F_t) = O_p(1)$, establishing~\eqref{eq:11}. The proofs
of \eqref{eq:12} and \eqref{eq:13} are similar.
\end{proof}
